---
title: "NoForLoopsWorks"
author: "Tess Attenborough"
date: "24 July 2018"
output: html_document
---
#here i am going to look by patient at shared clonotypes, if i can - for RBM.
---
title: "Adaption of Ben's code for looking at shared clonotypes"
author: "Tess Attenborough"
date: "24 July 2018"
output: html_document
---

# Load libraries
```{r}
library(data.table)
library(zoo)
library(plyr)
library(scales)
library(ggplot2)
library(ggthemes)
library(dplyr)
library(plotly)
library(pracma)
library(Hmisc)
library(rpart)
library(survminer)
library(knitr)
library(grid)
library(stringr)
library(ggrepel)
library(ggjoy)
library(RColorBrewer)
library(stringdist)
library(ape)
library(reshape2)
library(gplots)
library(ineq)
library(vegan)
library(Rtsne)
library(praise)
```

```{r}
#time point 

RBM1_alpha_CDR3 <- RBM1_alpha_dcr_cdr3_freq
RBM1_alpha_CDR3$Month <- "1"
RBM1_alpha_CDR3$Chain <- "alpha"

RBM3_alpha_CDR3 <- RBM3_alpha_dcr_cdr3_freq
RBM3_alpha_CDR3$Month <- "3"
RBM3_alpha_CDR3$Chain <- "alpha"

RBM2_alpha_CDR3 <- RBM2_alpha_dcr_cdr3_freq
RBM2_alpha_CDR3$Month <- "2"
RBM2_alpha_CDR3$Chain <- "alpha"


#not sure about this
#will try to join data frames
RBM_alpha <- rbind(RBM1_alpha_CDR3, RBM3_alpha_CDR3, RBM2_alpha_CDR3)
RBM_alpha$ID <- "RBM"
RBM_alpha$`CDR3 AA sequence` <- as.character(RBM_alpha$`CDR3 AA sequence`)
RBM_alpha$Month <- as.numeric(RBM_alpha$Month)
names(RBM_alpha)[names(RBM_alpha) == "CDR3 AA sequence"] <- "CDR3s"
names(RBM_alpha)[names(RBM_alpha) == "Number found in sample"] <- "Count"
dat=RBM_alpha

```


```{r}
dat$fillseq <- NA #creates a column for the 'colour number'

pie = dat[ order(dat$CDR3s, -dat$Count), ] #groups together clonotypes, lists them alphabetically and within clonotype sorts highest tp lowest

cherrypie = pie[!duplicated(pie$CDR3s), ] #deletes duplicates so largest exp is kept if clonotype appears more than once

goodcherrypie = cherrypie[ order(cherrypie$Month, -cherrypie$Count), ] #time points are in order, then within time points clonotypes are listed in reverse order

fillseq <- seq(1, length(goodcherrypie$CDR3s)) #make list of numbers corresponding with number of unique clonotypes

goodcherrypie$fillseq <- fillseq #add numbers from fillseq to data frame with unique clonotypes

goodcherrypie = goodcherrypie[ order(goodcherrypie$CDR3s), ] #reorders the clonotypes alphabetically (for similarity)

fillseq <- seq(1, length(goodcherrypie$Count)) #make list of numbers corresponding with number of unique clonotypes

goodcherrypie$fillseq <- fillseq #add numbers from fillseq to data frame with unique clonotypes


backToDat <- goodcherrypie[,c(1,6)] #make a dataframe with just cdr3seq and fillseq number

datWithFillseq <- merge(dat, backToDat, "CDR3s") #merge together so original data frame has correct fillseq number associated

datWithFillseq  <- datWithFillseq[,-6] #remove null column
names(datWithFillseq)[names(datWithFillseq) == 'fillseq.y'] <- 'fillseq' #rename column
#datWithFillseq  <- datWithFillseq[, c(2,3,4,1,5,6)] #reorder columns so they are the same as original order

#first we are making the dataset that will be used to compare clonotypes across all the samples
temp1 <- datWithFillseq[datWithFillseq$Month == "1",] #t1 first time point
temp2 <- datWithFillseq[datWithFillseq$Month == "2",] #t2 second time point
temp3 <- datWithFillseq[datWithFillseq$Month == "3",] #fourth time point

#intersectA <- temp2[temp2$CDR3s %in% temp1$CDR3s,] # overlap overlap( finds all the seqs in temp1 that also appear in temp 2)
#intersectB <- temp2[temp2$CDR3s %in% temp3$CDR3s,] # overlap overlap( finds all the seqs in temp1 that also appear in temp 2)
#intersectC <- temp3[temp3$CDR3s %in% temp4$CDR3s,] # overlap overlap( finds all the seqs in temp1 that also appear in temp 2)
        
        
#row <- c(dat$ID == "K", weekPosts["0"], weekPosts["12"], ((100/length(temp1$CDR3s)) * length(temp1$CDR3s[temp1$CDR3s %in% temp2$CDR3s])), ((100/length(temp2$CDR3s)) * length(temp2$CDR3s[temp2$CDR3s %in% temp1$CDR3s])), length(temp1$CDR3s), length(temp2$CDR3s), dat$chain == "a")
        
#shared <- rbind(shared, row)
#names(shared) <- c('ID', 'x1', 'x2', 'shared', 'sharedTo', 'x1clonotypes', 'x2clonotypes', 'chain')
        
        ### Shared clonotype plot ###
        # creates a vector identifying shared sequences
temp1$shared <- NA #creates column
temp2$shared <- NA
temp3$shared <- NA #creates column

temp1$shared[temp1$CDR3s %in% temp2$CDR3s | temp1$CDR3s %in% temp3$CDR3s] <- T # marks clonotypes that are in temp1 and also in temp2 OR temp 3 OR temp4  ETC as TRUE
temp1$shared[!temp1$CDR3s %in% temp2$CDR3s & !temp1$CDR3s %in% temp3$CDR3s] <- F # marks clonotypes that are in temp1 and NOT in temp2 OR temp3 OR temp4 ETC as FALSE

temp2$shared[temp2$CDR3s %in% temp1$CDR3s | temp2$CDR3s %in% temp3$CDR3s] <- T # marks clonotypes that are in temp2 and also in temp2 OR temp 3 OR temp4  ETC as TRUE
temp2$shared[!temp2$CDR3s %in% temp1$CDR3s & !temp2$CDR3s %in% temp3$CDR3s] <- F # marks clonotypes that are in temp2 and NOT in temp2 OR temp3 OR temp4 ETC as FALSE

temp3$shared[temp3$CDR3s %in% temp1$CDR3s | temp3$CDR3s %in% temp2$CDR3s] <- T # marks clonotypes that are in temp3 and also in temp3 OR temp 3 OR temp4  ETC as TRUE
temp3$shared[!temp3$CDR3s %in% temp1$CDR3s & !temp3$CDR3s %in% temp2$CDR3s] <- F # marks clonotypes that are in temp3 and NOT in temp3 OR temp3 OR temp4 ETC as FALSE

#testing to see if this the way
temp1$sharedintersect <- NA #creates column
temp2$sharedintersect <- NA
temp3$sharedintersect <- NA #creates column

#temp1$sharedintersect[temp1$CDR3s %in% temp2$CDR3s] <- T
#temp1$sharedintersect[!temp1$CDR3s %in% temp2$CDR3s] <- F #same for false
#temp2$sharedintersect[temp2$CDR3s %in% temp1$CDR3s] <- T
#temp2$sharedintersect[!temp2$CDR3s %in% temp1$CDR3s] <- F


temp1 <- arrange(temp1,desc(temp1$shared),temp1$fillseq) #orders the file first by seqs that are shared or not, then sorts by fillseq
temp2 <- arrange(temp2,desc(temp2$shared),temp2$fillseq)
temp3 <- arrange(temp3,desc(temp3$shared),temp3$fillseq)

  # vector to order and colour sequence
        #temp1$fillseq[temp1$shared == T] <- fillseq
        #temp1$fillseq[temp1$shared == F] <- length(temp1$fillseq[temp1$shared == T])+1
       # temp2$fillseq <- temp1$fillseq[match(temp2$CDR3s, temp1$CDR3s)]
        #temp2$fillseq[temp2$shared == F] <- length(temp2$fillseq[temp2$shared == T])+1
               

        # create 1 entry for all non-shared sequences
temp1.mod <- temp1 #duplicates temp1 and saves it as temp1.mod
temp2.mod <- temp2
temp3.mod <- temp3 #duplicates temp3 and saves it as temp3.mod

temp1.mod$Count[length(temp1.mod$ID)] <- sum(temp1.mod$Count[temp1.mod$shared == F]) # the last entry is given the frequency of all the non-shared clonotypes
temp2.mod$Count[length(temp2.mod$ID)] <- sum(temp2.mod$Count[temp2.mod$shared == F])
temp3.mod$Count[length(temp3.mod$ID)] <- sum(temp3.mod$Count[temp3.mod$shared == F]) # the last entry is given the frequency of all the non-shared clonotypes

#temp1.mod$Count[length(temp1.mod$ID)] <- sum(temp1.mod$Count[temp1.mod$sharedintersect == F]) # the last entry is given the frequency of all the non-shared clonotypes
#temp2.mod$Count[length(temp2.mod$ID)] <- sum(temp2.mod$Count[temp2.mod$sharedintersect == F])

temp1.mod$shared[length(temp1.mod$ID)] <- T #makes the last entry true so it is kept
temp2.mod$shared[length(temp2.mod$ID)] <- T
temp3.mod$shared[length(temp3.mod$ID)] <- T #makes the last entry true so it is kept

#temp1.mod$sharedintersect[length(temp1.mod$ID)] <- T #makes the last entry true so it is kept
#temp2.mod$sharedintersect[length(temp2.mod$ID)] <- T

temp1.mod <- temp1.mod[!temp1.mod$shared == F,] #gets rid of all non-shared clonotypes
temp2.mod <- temp2.mod[!temp2.mod$shared == F,]
temp3.mod <- temp3.mod[!temp3.mod$shared == F,] #gets rid of all non-shared clonotypes

#temp1.mod <- temp1.mod[!temp1.mod$sharedintersect == F,] #gets rid of all non-shared clonotypes
#temp2.mod <- temp2.mod[!temp2.mod$sharedintersect == F,]

temp1.mod$shared[length(temp1.mod$ID)] <- F #puts the last entry back to false
temp2.mod$shared[length(temp2.mod$ID)] <- F
temp3.mod$shared[length(temp3.mod$ID)] <- F #puts the last entry back to false


temp1.mod$fillseq[length(temp1.mod$ID)] <- 900000 #puts the last entry last in fillseq order
temp2.mod$fillseq[length(temp2.mod$ID)] <- 900000
temp3.mod$fillseq[length(temp3.mod$ID)] <- 900000 #puts the last entry back last in fillseq order

        # normalise sequence frequency
temp1.mod$Count <- (100/sum(temp1.mod$Count))*temp1.mod$Count #turns counts into percentages
temp2.mod$Count <- (100/sum(temp2.mod$Count))*temp2.mod$Count
temp3.mod$Count <- (100/sum(temp3.mod$Count))*temp3.mod$Count #turns counts into percentages


        
        #temp1.mod.expanded <- temp1.mod[rep(row.names(temp1.mod), temp1.mod$Count),]
        #temp2.mod.expanded <- temp2.mod[rep(row.names(temp2.mod), temp2.mod$Count),]
        
maxPcntShared <- max(c(100 - sum(temp1.mod$Count[temp1.mod$shared==T]), 100 - sum(temp2.mod$Count[temp2.mod$shared==T]), 100 - sum(temp3.mod$Count[temp3.mod$shared==T]))) #calculates highest % of uniques

minPcntShared <- min(c(100 - sum(temp1.mod$Count[temp1.mod$shared==T]), 100 - sum(temp2.mod$Count[temp2.mod$shared==T]), 100 - sum(temp3.mod$Count[temp3.mod$shared==T]))) #calculates lowest % of uniques (gives % of reads that come from clonotypes unique to the sample)
        
        # create x coordinates for line plotting
#temp1.mod$x <- 1.45 #new column all equalling 1.45
#temp2.mod$x <- 2.55 #new column all equalling 2.55
#temp3.mod$x <- 3.65 #new column all equalling 3.65
#temp4.mod$x <- 4.75 #new column all equalling 4.75

        # create x coordinates for line plotting
temp1.mod$x <- 3.65 #new column all equalling 1.45
temp2.mod$x <- 2.55 #new column all equalling 2.55
temp3.mod$x <- 1.45 #new column all equalling 3.65

        # create the y point for the plot
temp1.mod$y <- 100 - cumsum(temp1.mod$Count) + temp1.mod$Count #calculates y coordinate for each clonotype
temp2.mod$y <- 100 - cumsum(temp2.mod$Count) + temp2.mod$Count
temp3.mod$y <- 100 - cumsum(temp3.mod$Count) + temp3.mod$Count #calculates y coordinate for each clonotype

#collect relevant data
intersectA1 <- temp1.mod[temp1.mod$CDR3s %in% temp2.mod$CDR3s,] # overlap overlap( finds all the seqs in temp1 that also appear in temp 2)
intersectA2 <- temp2.mod[temp2.mod$CDR3s %in% temp1.mod$CDR3s,] # overlap overlap( finds all the seqs in temp1 that also appear in temp 2)
intersectB1 <- temp2.mod[temp2.mod$CDR3s %in% temp3.mod$CDR3s,] # overlap overlap( finds all the seqs in temp1 that also appear in temp 2)
intersectB2 <- temp3.mod[temp3.mod$CDR3s %in% temp2.mod$CDR3s,] # overlap overlap( finds all the seqs in temp1 that also appear in temp 2)

# merge the two datasets for plotting
intersectA.mod <- rbind(intersectA1, intersectA2)
intersectB.mod <- rbind(intersectB1, intersectB2)

yadjst <- 8 # so we can move around the not shared label
sampleName1 <- paste("K", unique(temp1.mod$Month), unique(temp1.mod$Chain), sep = '-') #makes the sample name
sampleName2 <- paste("K", unique(temp2.mod$Month), unique(temp2.mod$Chain), sep = '-')
sampleName3 <- paste("K", unique(temp3.mod$Month), unique(temp3.mod$Chain), sep = '-') #makes the sample name

```


     
ggp <- ggplot()+

geom_line(aes(x = intersectB.mod$x, y = intersectB.mod$y, group = intersectB.mod$fillseq), colour = 'grey', size = 0.1)+
geom_line(aes(x = intersectA.mod$x + 0.9, y = intersectA.mod$y, group = intersectA.mod$fillseq), colour = 'grey', size = 0.1)+
  geom_bar(aes(x = 1, temp3.mod$Count, fill = as.factor(temp3.mod$fillseq), alpha = as.factor(temp3.mod$shared)), stat = 'identity', colour = 'black', size = 0.1) +
geom_errorbar(aes(x = 1, ymin = round(minPcntShared-yadjst), ymax = round(minPcntShared-yadjst)))+
  geom_bar(aes(x = 3, temp2.mod$Count, fill = as.factor(temp2.mod$fillseq), alpha = as.factor(temp2.mod$shared)), stat = 'identity', colour = 'black', size = 0.1) +
geom_errorbar(aes(x = 3, ymin = round(minPcntShared-yadjst), ymax = round(minPcntShared-yadjst)))+
  geom_bar(aes(x = 5, temp1.mod$Count, fill = as.factor(temp1.mod$fillseq), alpha = as.factor(temp1.mod$shared)), stat = 'identity', colour = 'black', size = 0.1) +
geom_errorbar(aes(x = 5, ymin = round(minPcntShared-yadjst), ymax = round(minPcntShared-yadjst)))+
scale_alpha_manual(values=c(0, 1)) +
          #geom_errorbar(aes(x = 3, ymin = round(minPcntShared-yadjst), ymax = round(minPcntShared-yadjst)))+
          scale_y_continuous(breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100))+
          scale_x_continuous(breaks = c(1, 3, 5), labels = c(3, 2, 1))+
          geom_text(aes(x = 1, y = round(minPcntShared-yadjst/2)), label = '', size = 6)+
          geom_text(aes(x = 3, y = round(minPcntShared-yadjst/2)), label = '', size = 6)+
          geom_text(aes(x = 5, y = round(minPcntShared-yadjst/2)), label = '', size = 6)+
          annotate(geom = "segment", x = -Inf, xend = -Inf, y = -Inf, yend = Inf) +
          #annotate(geom = "segment", x = -Inf, xend = -Inf, y =  round(minPcntShared-yadjst), yend = round(minPcntShared, -1),
                   #linetype = "dashed", color = "white")+
          coord_flip(ylim=c(round(minPcntShared-yadjst), 100), expand = T) +
          labs(title = 'Shared Clonotypes: Patient K (alpha chain)', x = 'Month', y = 'Cumulative % of Sample')+
          theme(legend.position="none", panel.background = element_blank()) + guides(fill=FALSE)+ theme(
  axis.text = element_text(size = 30),text = element_text(size=30))
        
ggsave("K_alpha_betical.pdf", width = 40, height = 47, units = c('cm'))


ggp


